---
title: "Alcohol vs Seat choice"
author: "Onalee Garusinghe"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
   The median of the back boxplot is higher than both medians for the front and middle boxplots. The front median is slightly higher than the middle median. The outliers for the back boxplot goes farther than any of the front or middle outliers.
 
 
```{r}
plot(alcohol~Seat,data=davisdata)
```
  
## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
  The front and back seats hold about the same amount of people, while the back seat has more than double that amount of people. This summary tells us that even though the back seat had 32 people. they still brang 55 drinks, double the amount of the front row. The back rows average of drinks is 9.6, fron is 1.8 and middle is 3.3.  
  
## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
 The probability of getting these results are one out of ten thousand. So, a further investigation is required in order to find out which seats are different from the others.

## Conclusions


